DOpElib: A Goal Oriented Software Library for Computing PDEs and Optimization Problems

### 2012-10-05 Paper_May_2012/main.tex
Paper: Kapitel 2 fertig gestellt zum Gegenlesen

Generically, each problem in DOpElib is considered to be time-dependent and nonlinear because
these are the 'real' world problems. Therefore, (even for the linear and stationary Laplace equation),
we have to declare a (pseudo) time:
\begin{lstlisting}
  std::vector<double> times(1, 0.);
\end{lstlisting}
Then, the spatial mesh (here the unit square) is created and three-times globally-refined:
\begin{lstlisting}
  GridGenerator::hyper_cube(triangulation, 0, 1);
  triangulation.refine_global(3);
\end{lstlisting}
A major component which organizes the whole solution process (independent from 
the problem!) is the 
\begin{lstlisting}
MethodOfLines_StateSpaceTimeHandler<FE, DOFHANDLER, SPARSITYPATTERN, VECTOR, 2> DOFH(
      triangulation, state_fe);
\end{lstlisting}
This method handles all dofs in space and time and different versions exist
for forward as well as optimization problems.

@@

  P.SetDirichletBoundaryColors(0, comp_mask, &DD1);
\end{lstlisting}
Next, the solver for the linear equations needs to be specified:
\begin{lstlisting}
  SSolver solver(&P, "fullmem", pr, idc);
\end{lstlisting}
Finally, the ouput handler is initialized via
\begin{lstlisting}
  P.RegisterOutputHandler(&out);
  solver.RegisterOutputHandler(&out);
\end{lstlisting}
Finally, the programm is started with:
\begin{lstlisting}
      solver.ReInit();
      out.ReInit();
      out.Write(outp, 1, 1, 1);

      solver.ComputeReducedFunctionals();
\end{lstlisting}
After explaining the basic compononents that are necessary for all  
(linear and stationary) partial differential equations, we shall give 
an overview to the implementation of the specific form of the PDE. 
This step is done in the \texttt{localpde.h} file. As already explained,
each PDE is treatet in a nonlinear manner such that for solving 
the Laplace problem the following nonlinear step is necessary to recapitulate:
Find $\delta u\in V$:
\[
(\nabla \delta u, \nabla \phi) = -(\nabla u, \nabla \phi) 
\]
and $u^{n+1} = u^n + \delta u$ for $n=1,2,3,ldots$.
Therefore, the implementation reads for the right hand side:
\begin{lstlisting}
    void CellEquation(const CellDataContainer<dealii::DoFHandler<dealdim>, VECTOR, dealdim>& cdc,
                      dealii::Vector<double> &local_cell_vector,
                      double scale, double)
    {
      // implement (\nabla u, \nabla \phi) 
    }
\end{lstlisting}
Specifically,
\begin{lstlisting}
      for (unsigned int q_point = 0; q_point < n_q_points; q_point++)
      {
        Tensor<2, 2> ugrads;
        ugrads.clear();
        ugrads[0][0] = _ugrads[q_point][0][0];
        ugrads[0][1] = _ugrads[q_point][0][1];
        ugrads[1][0] = _ugrads[q_point][1][0];
        ugrads[1][1] = _ugrads[q_point][1][1];

	for (unsigned int i = 0; i < n_dofs_per_cell; i++)
        {
	  const Tensor<2, 2> phi_i_grads_u = state_fe_values[displacements].gradient(i, q_point);

          local_cell_vector(i) += scale * scalar_product(ugrads, phi_i_grads_u) 
	    * state_fe_values.JxW(q_point);
        }
      }
\end{lstlisting}
For the left hand side, we need to implement the Jacobian matrix:
\begin{lstlisting}
    void CellMatrix(const CellDataContainer<dealii::DoFHandler<dealdim>, VECTOR, dealdim>& cdc, FullMatrix<double> &local_entry_matrix, double, double)
    {
// implement  (\nabla \delta u, \nabla \phi)
}
\end{lstlisting}
Specifically,
\begin{lstlisting}
      for (unsigned int q_point = 0; q_point < n_q_points; q_point++)
      {
        for (unsigned int k = 0; k < n_dofs_per_cell; k++)
        {
          phi_grads_u[k] = state_fe_values[displacements].gradient(k, q_point);
        }

        for (unsigned int i = 0; i < n_dofs_per_cell; i++)
        {
          for (unsigned int j = 0; j < n_dofs_per_cell; j++)
          {
            local_entry_matrix(i, j) += scalar_product(phi_grads_u[j], phi_grads_u[i]) 
                * state_fe_values.JxW(q_point);
          }
        }
      }
\end{lstlisting}
The integration of the equation for each DoF and each quadrature point on each
cell is then done 
in the \texttt{templates/integrator.h} function.

The cost functional is now implemented in \todo{hier morgen weiter machen}

@@

\begin{lstlisting}
 void CellTimeEquation(const CellDataContainer<dealii::DoFHandler<dealdim>, VECTOR, dealdim>& cdc,
                           dealii::Vector<double> &local_cell_vector __attribute__((unused)),
		       double scale __attribute__((unused)))
    {
// implement (u^{n+1},\phi) 
}
\end{lstlisting}
and it is done in a straight-forward way:
\begin{lstlisting}
 for (unsigned int q_point=0;q_point<n_q_points;q_point++)
	{
	  Tensor<1,2> v;
	  u[0] = _uvalues[q_point](0);
	  u[1] = _uvalues[q_point](1);

	  for (unsigned int i=0;i<n_dofs_per_cell;i++)
	    {
	      const Tensor<1,2> phi_i_u = state_fe_values.value (i, q_point);

	      local_cell_vector(i) +=  scale * (u * phi_i_u) * state_fe_values.JxW(q_point);
	    }
	}
\end{lstlisting}
Here, the advantage is that DOpElib orders the terms in the timestepping
problems
such that only $(u^{n+1},\phi)$ must be implemented. However, if someone 
needs explicit input of the old timestep term, then he can use 
\begin{lstlisting}
 void CellTimeEquationExplicit (const CellDataContainer<dealii::DoFHandler<dealdim>, VECTOR, dealdim>& cdc,
                           dealii::Vector<double> &local_cell_vector,
				   double scale)
    {
      // implement (u^{n+1},\phi) and (u^n,\phi)  
    }
    \end{lstlisting}
    For instance, this explicit term is used for fluid-structure interaction in
    which
    the old timestep term needs explicit modification.

@@

Concretely, let us focus on the Laplace equation and ...

this is taken from step-2 in the Opt examples.

\todo{Optimality system}

\todo{Two problems in which we identify the different terms and implementation 
of these terms in DOpE}

@@

%\subsection{Optimization algorithms}
%Now, in order to solve optimization algorithms we need to define some algorithms.
%At present we offer a selection of algorithms that solve the reduced optimization 
%problem where the PDE constraint has been eliminated as explained in the previous section.
%\item \texttt{opt\underline{ }algorithms/reducedalgorithm.h} An interface for all 
%  optimization problems in the reduced formulation. It offers some test functionality
%  to assert that the derivatives of the problem are computed correctly.
%\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithm.h}
%  A line-search Newton algorithm using a cg method to invert the reduced hessian. 
%  Implementation ignores any additional constraints.
%\item \texttt{opt\underline{ }algorithms/reducedtrustregionnewton.h}
%  A trust region Newton algorithm using a cg method to invert the reduced hessian.
%  Implementation ignores any additional constraints.
%\item \texttt{opt\underline{ }algorithms/reduced\underline{ }snopt\underline{ }algorithm.h}
%  An algorithm to solve reduced optimization problems with additional control constraints.
%  ((reduced) state constraints are not yet implemented.)
%\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithmwithinverse.h}
%  Line-search Newton algorithm that assumes there exists a method in the reduced problem
%  that can invert the reduced hessian. (This usually makes sense only if there is no 
%  PDE constraint.)
%\item \texttt{opt\underline{ }algorithms/generalized\underline{ }mma\underline{ }algorithm.h}
%  An implementation of the MMA-Algorithm for structural optimization using an augmented
%  Lagrangian formulation for the subproblems. The subproblem is implemented using the 
%  special purpose file
%  \texttt{include/augmentedlagrangianproblem.h}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Interfaces to other software packages}
%Since DOpE uses as basis the software library deal.II, all its interfaces
%to other packages can be accessed to. For instance, such libararies 
%are trilinos for with an algebraic multigrid method, MPI for a parallel
%solution of the problem.
%In addition DOpE itself has an interface to SNOPT.
%%\section{Documentation, Code Development, Webpage}
%%\label{documentation}
%%At the present step, the DOpElib project comes with 
%%an detailed documentation of all features and examples 
%%in pdf format and an detailed programming code 
%%documentation. 
%%
%%\todo{License? How to access to DOpE?}
%%\todo{Name of the website}
%%
%%In addition, the DOpElib test suite provides some regression tests. 
%%They are run to compare 
%%the output to previous outputs. This is useful (necessary) after 
%%changing programming code anywhere in the library. If a test
%%succeeds, everything is fine in the library. If not, you should not
%%check in your code into DOpE. Please make sure what is going wrong and WHY!
%%Every command is computed via a Makefile. 
%%
\section{Applications}
\label{applications}
We present three numerical tests which demonstrate different
features of DOpElib:
\item In the first numerical example, we consider 
goal-oriented mesh refinement with the help of the 
Dual-Weighted-Residual (DWR) method for the stationary Navier-Stokes equations.
\item The second example presents nonstationary fluid-structure 
interaction. The challenges for those kind of problems are the multi-domain
character of the coupled problem and the treatment of the coupling conditions.
The problem is formulated in a variational monolithically-coupled way which 
allows to consider goal-oriented mesh refinement and gradient-based optimization.
\item In the third numerical test, an optmization problem for structural mechanics
is discussed.

@@

The configuration is 
sketched in Figure \ref{configuration_csm_and_fsi_2D}. Details 
on parameters and evaluation functionals and other results 
can be found in \cite{HrTu06b, BuSc06, TuHrMaRaWoAc10, DeHaeAnnBrVie10, Wi11}. 
The Fractional-Step-$\theta$ scheme is used for time discretization with
different time step sizes $k$. However, the time stepping scheme can be 
very easily chosen in the \texttt{main.cc} function by declaring
\begin{lstlisting}
#define TSP1 ForwardEulerProblem
#define TSP2 BackwardEulerProblem
#define TSP3 CrankNicolsonProblem
#define TSP4 ShiftedCrankNicolsonProblem
#define TSP5 FractionalStepThetaProblem
\end{lstlisting}
and then using the designated scheme.

>>>>

Generically, each problem in DOpElib is considered to be time-dependent and nonlinear because
these are the 'real' world problems. Therefore, (even for the linear and stationary Laplace equation),
we have to declare a (pseudo) time:
\begin{lstlisting}
  std::vector<double> times(1, 0.);
\end{lstlisting}
Then, the spatial mesh (here the unit square) is created and three-times globally-refined:
\begin{lstlisting}
  GridGenerator::hyper_cube(triangulation, 0, 1);
  triangulation.refine_global(3);
\end{lstlisting}
A major component which organizes the whole solution process (independent from 
the problem!) is the 
\begin{lstlisting}
  MethodOfLines_StateSpaceTimeHandler<FE, DOFHANDLER, 
    SPARSITYPATTERN, VECTOR, 2> DOFH(triangulation, state_fe);
\end{lstlisting}
This method handles all dofs in space and time and different versions exist
for forward as well as optimization problems.

@@

  P.SetDirichletBoundaryColors(0, comp_mask, &DD1);
\end{lstlisting}
Next, the solver for the linear equations needs to be specified:
\begin{lstlisting}
  SSolver solver(&P, "fullmem", pr, idc);
\end{lstlisting}
Finally, the ouput handler is initialized via
\begin{lstlisting}
  P.RegisterOutputHandler(&out);
  solver.RegisterOutputHandler(&out);
\end{lstlisting}
Finally, the programm is started with:
\begin{lstlisting}
  solver.ReInit();
  out.ReInit();
  out.Write(outp, 1, 1, 1);
  solver.ComputeReducedFunctionals();
\end{lstlisting}
After explaining the basic compononents that are necessary for all  
(linear and stationary) partial differential equations, we shall give 
an overview to the implementation of the specific form of the PDE. 
This step is done in the \texttt{localpde.h} file. As already explained,
each PDE is treatet in a nonlinear manner such that for solving 
the Laplace problem the following nonlinear step is necessary to recapitulate:
Find $\delta u\in V$:
\[
(\nabla \delta u, \nabla \phi) = -(\nabla u, \nabla \phi) 
\]
and $u^{n+1} = u^n + \delta u$ for $n=1,2,3,ldots$.
Therefore, the implementation reads for the right hand side:
\begin{lstlisting}
   void CellEquation(...)
    {
      // implement (\nabla u, \nabla \phi) 
    }
\end{lstlisting}
Specifically, the inner loops reads
\begin{lstlisting}
   for (all quadrature points per cell q)
      {
        Tensor<2, 2> ugrads; // solution vector

	for (all dofs per cell i)
        {
	  const Tensor<2, 2> phi_i_grads_u; // test function

          local_cell_vector(i) += scale * 
            scalar_product(ugrads, phi_i_grads_u) *
	    state_fe_values.JxW(q_point);
        }
      }
\end{lstlisting}
For the left hand side, we need to implement the Jacobian matrix:
\begin{lstlisting}
   void CellMatrix(...)
    {
      // implement  (\nabla \delta u, \nabla \phi)
    }
\end{lstlisting}
Specifically,
\begin{lstlisting}
      for (all quadrature points per cell q)      
        for (all dofs per cell i)    
          for (all dofs per cell j)
          {
            local_entry_matrix(i, j) += 
              scalar_product(phi_grads_u[j], phi_grads_u[i]) * 
              state_fe_values.JxW(q_point);
          }
\end{lstlisting}
The integration of the equation for each DoF and each quadrature point on each
cell is then done 
in the \texttt{templates/integrator.h} function.

The target functional 
is now implemented in \texttt{functional.h} and 
treats a point evaluation:
\begin{lstlisting}
  double PointValue(...)
   {
    Point<2> p1(0.5, 0.5);
    Vector<double> tmp_vector(2);
    // more stuff is necessary here
    VectorTools::point_value (...);
    double x = tmp_vector(0);

    return x;
   }
\end{lstlisting}

@@

\begin{lstlisting}
  void CellTimeEquation(...)
   {
     // implement (u^{n+1},\phi) 
   }
\end{lstlisting}
and it is done in a straight-forward way:
\begin{lstlisting}
  for (all quadrature points per cell q)
   {
     Tensor<1,2> u = ...;

     for (all dofs per cell i)
      {
        const Tensor<1,2> phi_i_u = ...;

        local_cell_vector(i) +=  
          scale * (u * phi_i_u) * 
          state_fe_values.JxW(q_point);
      }
   }
\end{lstlisting}
Here, the advantage is that DOpElib orders the terms in the timestepping
problems
such that only $(u^{n+1},\phi)$ must be implemented. However, if someone 
needs explicit input of the old timestep term, then he can use 
\begin{lstlisting}
  void CellTimeEquationExplicit (...)
   {
     // implement (u^{n+1},\phi) and (u^n,\phi)  
   }
\end{lstlisting}
For instance, this explicit term is used for fluid-structure interaction in
which
the old timestep term needs explicit modification.

@@

Concretely, let us focus on the Laplace equation and 
the following optimization problem (taken from 
Example 2) in \texttt{Examples/OPT/StatPDE}:
\begin{align*}
\min_{(q,u)\in \mathbb R^3 \times H_0^1(\Omega; \mathbb R^2)} J(q,u) &=
\frac{1}{2} \sum_{i=0}^2 |(u-\overline u)(x_i)|^2 + \frac{\alpha}{2}\|q\|^2\\
\text{s.t.} (\nabla u,\nabla \phi) &= (f(q),\phi)\;\;\forall\,\phi \in H^1_0(\Omega; \mathbb R^2)
\end{align*}
on the domain $\Omega = [0,1]^2$, with
\item the observation points
\begin{align*}
x_0 = (0.5, 0.5), \quad x_1 = (0.5, 0.25),\quad x_2 = (0.25, 0.25),
\end{align*}
\item the regularization parameter $\alpha = 0$, 
\item the right hand side
\begin{align*}
 f(q) &= q_0 \left(\begin{matrix}2\pi^2  \sin( \pi x) \sin(\pi y)\\0 \end{matrix}\right)\\
      &+ q_1 \left(\begin{matrix}5\pi^2  \sin( \pi x) \sin(2\pi y)\\0 \end{matrix}\right)\\
      &+ q_2 \left(\begin{matrix}0 \\8\pi^2  \sin(2\pi x) \sin(2\pi y)\end{matrix}\right)\\
\end{align*}
\item and the exact solution given by 
\begin{align*}
 \overline{q} &= \bigl(1;0.5;1\bigr)\\
 \overline{u}& = \left(\begin{matrix} \sin( \pi x)( \sin(\pi y)+0.5\sin(2\pi y))\\\sin(2\pi x) \sin(2\pi y) \end{matrix}\right).
\end{align*}
\begin{defi}[Constrained optimization]
\label{problem_constraint_optimization}
Minimize the cost functional $J(q,U)$ subject to the state equation
$A(q,U)(\Phi) = 0$ (as defined
in~\eqref{state_form} and~\eqref{opt_state_equation}) for $(q,U) \in 
Q\times  \{v_D+{\cal X}\}$. 
\end{defi}
The constrained optimization problem  on the space $Q_d\times {\cal X}$ 
is reformulated into an unconstrained optimization problem on the
space $Q_d$. Therefore, we assume the existence of the solution operator  
$S:Q_d\rightarrow {v_D+{\cal X}}$ with a unique solution
$U=S(q)$. Herewith, we define the reduced cost functional
$j:Q_d\rightarrow \mathbb{R}$ by 
\begin{equation}
  \label{opt_reduced_functional}
  j(q) := J(q,S(q)) .
\end{equation}
Newton's method to solve Problem~\ref{opt_reduced_problem} reads:
For $l=0,1,\ldots,$ solve
\begin{equation}
\label{opt_newton_method}
\begin{aligned}
j''(q^l)(\delta q , \tau q) &= -j'(q^l)(\delta q) 
\quad\forall\tau q\in Q_d, \\
q^{l+1} &= q^l + \omega\delta q,
\end{aligned} 
\end{equation}
with a line search parameter $\omega\in (0,1]$ which 
will be specified in Algorithm \ref{algo_opt}.
Specifically, the residual and the Hessian of Newton's method 
\eqref{opt_newton_method}
can be computed with the help of the following two results:
\begin{proposition}[Residual of Newton's method]
\label{prop_newton_residual}
Let $q\in Q_d, U=S(q)\in {\cal X}$
and $Z\in {\cal X}$ the dual solution be obtained after solving 
the first and second equation of the KKT system 
\eqref{opt_KKT_system}. 
Then the residual of Newton's method \eqref{opt_newton_method} 
is defined as
\begin{equation*}
j'(q)(\delta q) := {\cal L}'_{q}(q,U,Z)(\delta q),
\end{equation*}
i.e., in explicit representation
\begin{equation*}
j'(q)(\delta q) := \alpha_T (q , \tau q)_Q - 
A_{q}'(q,U)(\tau q , Z).
\end{equation*}
\end{proposition}
\begin{proof}
The proof uses standard techniques. Details can be found in  
\cite{BeMeVe06}.
\end{proof}
\begin{proposition}[Hessian of Newton's method]
  \label{prop_newton_hessian}
  Let $q\in Q_d, U=S(q)\in {\cal X}$ and $Z\in {\cal X}$ and  $\delta
  q\in Q_d$ be given. Further, let $\delta U\in {\cal X}$ be the
  solution of the tangent problem 
  \[
  \delta U\in{\cal X},\quad 
  A_{U}'(q,U)(\delta U , \Phi) 
  = -A_{q}'(q,U)(\delta q , \Phi)  \quad\forall \Phi\in {\cal
    X},
  \]
  and $\delta Z\in {\cal X}$ the solution of the adjoint Hessian 
  problem  
  \[
  A_{U}'(q,U)(\Phi, \delta Z)
  = J''_{UU}(q,U)(\delta U, \Phi)
  - A_{UU}''(q,U)(\delta U, \Phi, Z)
  - A_{qU}''(q,U)(\delta q , \Phi, Z)  \quad\forall \Phi\in
  {\cal X}. 
  \]
 Then it holds  for all $\tau q\in Q_d$:
  \[
  j''(q)(\delta q, \tau q):= 
  \alpha_T (\delta q , \tau q)_Q -
  A_{qq}''(q, U)(\delta q, \tau q , Z) -
  A_{Uq}''(q,U)(\delta U, \tau q , Z) -
  A_{q}'(q,U)(\tau q , \delta Z).
  \]
\end{proposition}
\begin{proof}
  For the proof this statement (including its time-dependent version), we refer to 
  Becker et al. \cite{BeMeVe06}.
  The stationary version of this proposition is easily derived by neglecting 
  all time derivatives, which concludes the assertion. 
\end{proof}
The implementation of all previous terms 
is realized in the \texttt{localpde.h} file.
As an example, we examine the adjoint 
\begin{equation}
  \label{opt_KKT_system}
  \begin{aligned}
    A_{U}'(q,U)(\Phi , Z) &= J'_{U}(q,U)(\Phi) & \forall \Phi&\in {\cal X},
  \end{aligned}
\end{equation}

The implementation it split into equation terms, i.e., 
\begin{lstlisting} 
  void CellEquation_U(...)
   {
     // implement (\nabla \phi, \nabla z)
   }
\end{lstlisting}
and functional terms, i.e.,     
\begin{lstlisting} 
  virtual void PointValue_U(...)
      {
        // implement here the derivative of 
        // the point cost functional
      }
\end{lstlisting}
All remaining terms of the previous two propositions 
are implemented in the same manner.

Afterwards, it remains to use an appropriate 
optimization algorithm in order to solve the 
problem. At present we offer a selection of algorithms that solve the reduced optimization 
problem where the PDE constraint has been eliminated as explained previously.
\begin{itemize}
\item \texttt{opt\underline{ }algorithms/reducedalgorithm.h} An interface for all 
  optimization problems in the reduced formulation. It offers some test functionality
  to assert that the derivatives of the problem are computed correctly.
\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithm.h}
  A line-search Newton algorithm using a cg method to invert the reduced hessian. 
  Implementation ignores any additional constraints.
\item \texttt{opt\underline{ }algorithms/reducedtrustregionnewton.h}
  A trust region Newton algorithm using a cg method to invert the reduced hessian.
  Implementation ignores any additional constraints.
\item \texttt{opt\underline{ }algorithms/reduced\underline{ }snopt\underline{ }algorithm.h}
  An algorithm to solve reduced optimization problems with additional control constraints.
  ((reduced) state constraints are not yet implemented.)
\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithmwithinverse.h}
  Line-search Newton algorithm that assumes there exists a method in the reduced problem
  that can invert the reduced hessian. (This usually makes sense only if there is no 
  PDE constraint.)
\item \texttt{opt\underline{ }algorithms/generalized\underline{ }mma\underline{ }algorithm.h}
  An implementation of the MMA-Algorithm for structural optimization using an augmented
  Lagrangian formulation for the subproblems. The subproblem is implemented using the 
  special purpose file
  \texttt{include/augmentedlagrangianproblem.h}.
\end{itemize}

@@

%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\subsection{Interfaces to other software packages}
%Since DOpE uses as basis the software library deal.II, all its interfaces
%to other packages can be accessed to. For instance, such libararies 
%are trilinos for with an algebraic multigrid method, MPI for a parallel
%solution of the problem.
%
%In addition DOpE itself has an interface to SNOPT.
%
%%\section{Documentation, Code Development, Webpage}
%%\label{documentation}
%%At the present step, the DOpElib project comes with 
%%an detailed documentation of all features and examples 
%%in pdf format and an detailed programming code 
%%documentation. 
%%
%%\todo{License? How to access to DOpE?}
%%\todo{Name of the website}
%%
%%In addition, the DOpElib test suite provides some regression tests. 
%%They are run to compare 
%%the output to previous outputs. This is useful (necessary) after 
%%changing programming code anywhere in the library. If a test
%%succeeds, everything is fine in the library. If not, you should not
%%check in your code into DOpE. Please make sure what is going wrong and WHY!
%%Every command is computed via a Makefile. 
%%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Applications}
\label{applications}
We present three numerical tests which demonstrate different
features of DOpElib:
\begin{itemize}
\item In the first numerical example, we consider 
goal-oriented mesh refinement with the help of the 
Dual-Weighted-Residual (DWR) method for the stationary Navier-Stokes equations.
\item The second example presents nonstationary fluid-structure 
interaction. The challenges for those kind of problems are the multi-domain
character of the coupled problem and the treatment of the coupling conditions.
The problem is formulated in a variational monolithically-coupled way which 
allows to consider goal-oriented mesh refinement and gradient-based optimization.
\item In the third numerical test, an optmization problem for structural mechanics
is discussed.
\end{itemize}

@@

The configuration is 
sketched in Figure \ref{configuration_csm_and_fsi_2D}. Details 
on parameters and evaluation functionals and other results 
can be found in \cite{HrTu06b, BuSc06, TuHrMaRaWoAc10, DeHaeAnnBrVie10, Wi11}. 
The Fractional-Step-$\theta$ scheme is used for time discretization with
different time step sizes $k$. However, the time stepping scheme can be 
very easily chosen in the \texttt{main.cc} function by declaring
\begin{lstlisting}
#define TSP1 ForwardEulerProblem
#define TSP2 BackwardEulerProblem
#define TSP3 CrankNicolsonProblem
#define TSP4 ShiftedCrankNicolsonProblem
#define TSP5 FractionalStepThetaProblem
\end{lstlisting}
and then using in the code the designated scheme, 
for example here the Fractional-Step-$\theta$ scheme
\texttt{TSP5}.
